When Do You Repeat Yourself?\\ Voices from the Trenches of Linux Kernel Maintainers on Code Duplication

### 2025-10-29 papers/techdebt2026/techdebt.tex
techdebt2026: techdebt: better style DRY highlight box
The DRY box contained a nested colon (foo: is bar and bar: is foobar)
and a full stop after the quote. Fix both by styling the DRY box to
remove this colon, and take the opportunity to insert the full stop
inside the quote.

Signed-off-by: David Tadokoro <davidbtadokoro@usp.br>

%% DRY Highlight Box %%
\newenvironment{dry-highlight-box}[1]{%
  \begin{tcolorbox}[colback=blue!5!white, colframe=blue!60!black, boxrule=0.5pt,
                    left=1mm, right=1mm, top=1mm, bottom=1mm, sharp corners]
  \textbf{#1:} \itshape}{\end{tcolorbox}}
%% DRY Highlight Box %%

@@

\begin{dry-highlight-box}{DRY principle}
  ``We feel that the only way to develop software reliably, and to make our
  developments easier to understand and maintain, is to follow what we call the
  DRY principle: Every piece of knowledge must have a single, unambiguous,
  authoritative representation within a system''.
\end{dry-highlight-box}

>>>>

%% DRY Highlight Box %%
\newenvironment{dry-highlight-box}[1]{%
  \begin{tcolorbox}[colback=blue!5!white, colframe=blue!60!black, boxrule=0.5pt,
                    left=1mm, right=1mm, top=1mm, bottom=1mm, sharp corners]
    \textbf{[#1]} \itshape}{\end{tcolorbox}}
%% DRY Highlight Box %%

@@

\begin{dry-highlight-box}{DRY principle}
  ``We feel that the only way to develop software reliably, and to make our
  developments easier to understand and maintain, is to follow what we call the
  DRY principle: Every piece of knowledge must have a single, unambiguous,
  authoritative representation within a system.''
\end{dry-highlight-box}
